The importance of alternatives in scalar implicature

### 2016-01-21 Paper/Paper.Rmd
Added final model fit plot

```{r}
speakers <- bind_rows(speakerE12 %>% mutate(expt = "4"), 
                      speakerE10 %>% mutate(expt = "3a"), 
                      speakerE8 %>% mutate(expt = "1a"))
# ggplot(speakers, 
#        aes(x = stars, y = speaker.p, col = degree, lty = expt)) + 
#   geom_line() + 
#   facet_grid(.~ scale) + 
#   theme_bw()
```

@@

Experiment 1a and 1b were conducted to approximate literal listener semantic distributions (1a) and pragmatic judgments (1b) for five pairs of scalar items taken from van Tiel (2014) (see figure 5 for stimuli). Each pair consists of a "weaker" scalar term (e.g. "some") and a stronger scalar term (e.g. "all"). We are calling these "entialment scales"", because they encode the assumption that a listener need only have a the stronger alternative present to generate an enriched interpretation of the weaker term.

@@

### Participants
Participants for both tasks were recruited on Amazon Mechanical Turk and paid $0.20 for their participation. Thirty participants were recruited for Experiment 1a. Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N. Fifty participants were recruited for experiment 1b. Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.

### Design and procedure
The left panel of Figure 1 shows a screen shot of a trial from Experiment 1a. Participants were presented with a target scalar item and a star-rating (between 1-5 stars) and asked to judge the compatibility of the scalar item and star-rating. Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person \___ed the food?" where a target scalar was presented in the "\___ed." Each participant was presented all scalar item and star-rating combinations with randomization.

The right panel of Figure 1 shows a screen shot of a trial from Experiment 1b. On each trial, participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they \___ed the food." They were then asked to generate a star-rating according to what they think the reviewer likely gave. Each participant was presented all scalar items with randomization.

The left panel of figure two shows literal semantics for each of the scalar terms "liked" and "loved" as distributions over star-ratings.

Chi-squared test? Null results, not really important here anyway...
```{r}
# chisq.test(subset(speakerE8, degree == "hi" & scale == "memorable_unforgettable")$speaker.p,
#            subset(speakerE8, degree == "low" & scale == "memorable_unforgettable")$speaker.p)
# subset(speakerE8, degree == "low")$cnt.judgment
# chisq.test(subset(speakerE8, degree == "hi")$cnt.judgment,
#            subset(speakerE8, degree == "low")$cnt.judgment)
```

```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=7, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel plots literal semantic distributions for the scalar pair \'liked/loved\'. The y-axis is the percentage of \'yes\' responses for a scalar term that is compatibible with the number of stars on the x-axis (ie 100\\% of respondents beleived that \'liked\' was compatible with both 4 and 5 stars). Erro bars are 95\\% confidence intervals. The right panel plots pragmatic judgments for the scalar pair \'liked/loved\'. The y-axis is the proportion of selection of the star-rating on the x-axis (ie over 80\\% of judgments when prompted with \'loved\' were 5-stars)."}

plotData <- speakerE8 %>%
  mutate(degree = ifelse(degree == "hi", "loved", "liked"))

# Literal listener: Entailment (e8)
e6Plot <- ggplot(data = subset(plotData, scale == "liked_loved"), aes(x = stars, y = speaker.p, col=degree)) +
  geom_line() +
  ylab("Percent yes") +
  geom_linerange(aes(ymin = speaker.p - cil, 
                     ymax = speaker.p + cih)) +
  ggtitle("Literal semantics")

# Pragmatic listener: Entailment (e6)
plotData <- listenerE6 %>%
  mutate(degree = ifelse(degree == "hi", "loved", "liked"))
e8Plot <- ggplot(data = subset(plotData, scale == "liked_loved"),
                 aes(x = stars, y = listener.p, fill = degree)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~degree) +
  ylab("Proportion of star-ratings chosen") +
  ggtitle("Pragmatic judgments") +
  theme(legend.position="none")

gridExtra::grid.arrange(e6Plot, e8Plot, ncol = 2, widths = c(2.5,3))
```

@@

In Experiment 2 we asked participants to generate plausible alternatives for the scalar items presented in Experiment 1.

@@

Using Amazon's Mechanical Turk, N workers were paid $0.20 to participate. n workers were dropped from the analysis because they either failed to pass training trials or were not native English speakers. The final sample was N workers, all of whom  were naive to the purpose of the experiment.

### Design and procedure
Participants were presented a target scalar term embedded in a sentence such as, "In a recent restaurant review someone said they thought they *----*ed the food." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of *----*?" and asked to generate three alternatives.

## Results and Discussion
Figure 3 plots the combined counts of alternatives generated for the scalar items "liked" and "loved." Alternative distributions for the other scalar pairs (e.g.. "good/excellent", "memorable/unforgettable") were similarly long-tailed. In Experiments 3a,b we took the top two alternatives generated for each scalar item to enrich the entailment only scales from Experiments 1a,b. In experiment 4 we further enriched the scales from Experiments 3a,b with a neutral valence scalar chosen from the alternative sets.

@@

Experiment 3a,b are identical to Experiments 1a,b except the set of target scalar was expanded to include the top two alternatives generated for each scalar family. The orange colored items in table 1 denote additional scalar items added in Experiments 3a,b.

@@

Participants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation. Thirty participants were recruited for Experiment 3a (Literal Listener task). Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.

Fifty participants were recruited for Experiment 3b (Pragmatic Listener task). Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.

@@

## Results and Discussion
Distributional differences.

# Experiment 4: Symmetric scales
Experiment 4a is identical to Experiments 1a and 3a except the set of target scalar was expanded to include a neutral valence scalar item for each scalar family. The purple colored items in Table 1 denote additional scalar items added in Experiments 4.

Participants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation. Thirty participants were recruited for Experiment 4 (Literal Listener task). Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.

@@

## Results and Discussion
Distributional differences.

# Temp section Model was here

### Results
Table here

Figure 4 plots model / human correlation for our three simulations. Alpha was tuned separately for each of these runs...
```{r performancePlots, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items. Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b. The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b."}
# Tuned model run data
plotData <- allModelRunData %>%
  mutate(study = ifelse(numAlts == 5, "Symmetric", 
                        ifelse(numAlts == 4, "Neg_alts", "Entailment"))) %>%
  gather(Experiment, cors, c(corE6, corE11)) %>%
  mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))

@@

# Correlation scatter plot
symmetricCorPlot <- ggplot(subset(plotData, study == "Symmetric"), aes(x = listener.p, y = preds)) + 
  geom_point() +
  xlab("Model predictions") +
  ylab("Human judgments") +
  stat_smooth(method = "lm") + 
  ggtitle("Model fit\nSymmetric scale")

corBarChart
# gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))
```

>>>>

@@

Experiment 1a and 1b were conducted to approximate literal listener semantic distributions $p_{L0}(m|u)$ (Exerpiment 1a) and pragmatic judgments $p_{L1}(m|u)$ (Experiment 1b) for five pairs of scalar items taken from van Tiel (2014) (see figure 5 for stimuli). Each pair consists of a "weaker" scalar term (e.g. "some") and a stronger scalar term (e.g. "all"). We are calling these "entialment scales"", because they encode the assumption that a listener need only have a the stronger alternative present to generate an enriched interpretation of the weaker term. The grey colored items in Table 1 denote the original "entailment" items used in Experiments 1a,b.

@@

### Participants
Participants for both tasks were recruited on Amazon Mechanical Turk and paid $0.20 for their participation. Thirty participants were recruited for Experiment 1a. Data for two participants was thrown out during analysis because there were not native English speakers, leaving a total sample of 28 participants. Fifty participants were recruited for experiment 1b. Data for 7 participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 43 participants.

### Design and procedure
The left panel of Figure 1 shows a screen shot of a trial from Experiment 1a. Participants were presented with a target scalar item and a star-rating (between 1-5 stars) and asked to judge the compatibility of the scalar item and star-rating. Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the "\____." Each participant was presented all scalar item and star-rating combinations with randomization.

The right panel of Figure 1 shows a screen shot of a trial from Experiment 1b. On each trial, participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star-rating according to what they thought the reviewer likely gave. Each participant was presented all scalar items with randomization.

## Results and Discussion
Figure 2 plots literal listner $p_{L0}(m|u)$ distributions obtained in Experiments 1a, 3a and 4. Data from 1a is (...). We see clear variation between semantic judgments between scalar families in all the Experiments. For example, compatibility judgments for "memorable" and "forgettable" are more similar than those for "good / excellent" or "liked / loved". We will address distributional similarity across the studies in later sections.

```{r}
# chisq.test(subset(speakerE8, degree == "hi" & scale == "memorable_unforgettable")$speaker.p,
#            subset(speakerE8, degree == "low" & scale == "memorable_unforgettable")$speaker.p)
# subset(speakerE8, degree == "low")$cnt.judgment
# chisq.test(subset(speakerE8, degree == "hi")$cnt.judgment,
#            subset(speakerE8, degree == "low")$cnt.judgment)
```

```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel plots literal semantic distributions for the scalar pair \'liked/loved\'. The y-axis is the percentage of \'yes\' responses for a scalar term that is compatibible with the number of stars on the x-axis (ie 100\\% of respondents beleived that \'liked\' was compatible with both 4 and 5 stars). Erro bars are 95\\% confidence intervals. The right panel plots pragmatic judgments for the scalar pair \'liked/loved\'. The y-axis is the proportion of selection of the star-rating on the x-axis (ie over 80\\% of judgments when prompted with \'loved\' were 5-stars)."}

speakers <- bind_rows(speakerE12 %>% mutate(expt = "4"), 
                      speakerE10 %>% mutate(expt = "3a"), 
                      speakerE8 %>% mutate(expt = "1a"))

ggplot(speakers, 
       aes(x = stars, y = speaker.p, col = degree, lty = expt)) + 
  geom_line() + 
  facet_grid(.~ scale) + 
  theme_bw()

####################################
# OLD PLOTS -------------------------
# plotData <- speakerE8 %>%
#   mutate(degree = ifelse(degree == "hi", "loved", "liked"))
# # Literal listener: Entailment (e8)
# e6Plot <- ggplot(data = subset(plotData, scale == "liked_loved"), aes(x = stars, y = speaker.p, col=degree)) +
#   geom_line() +
#   ylab("Percent yes") +
#   geom_linerange(aes(ymin = speaker.p - cil, 
#                      ymax = speaker.p + cih)) +
#   ggtitle("Literal semantics")
# 
# # Pragmatic listener: Entailment (e6)
# plotData <- listenerE6 %>%
#   mutate(degree = ifelse(degree == "hi", "loved", "liked"))
# e8Plot <- ggplot(data = subset(plotData, scale == "liked_loved"),
#                  aes(x = stars, y = listener.p, fill = degree)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   facet_wrap(~degree) +
#   ylab("Proportion of star-ratings chosen") +
#   ggtitle("Pragmatic judgments") +
#   theme(legend.position="none")
# gridExtra::grid.arrange(e6Plot, e8Plot, ncol = 2, widths = c(2.5,3))
```

@@

In Experiment 1 we obtained literal semantic compatibility and pragmatic judgments for five pairs of scalar terms. We would like to extend the scale descriptions for each of these pairs to include other plausible alternatives. We chose to take an empirical approach rather than assign alternatives arbitrarily. We adopted a modified cloze task, inspired by Experiment 2 in van Tiel (2014) and asked participants to generate alternatives for us.

@@

Using Amazon's Mechanical Turk, 30 workers were paid $0.20 to participate. All participants were native English speakers and naive to the purpose of the experiment.

### Design and procedure
Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____" with a target scalar presented in the "\____." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" and asked to generate three unique alternatives.

## Results and Discussion
Figure 3 plots the combined counts of alternatives generated for the scalar items "liked" and "loved." Alternative distributions for the other scalar pairs (e.g.. "good/excellent", "memorable/unforgettable") were similarly long-tailed, however the size and content of the alternate sets were diverse. (SOMETHING MORE MORE FORMAL HERE???)

@@

In Exerpiment 1a,b we measured literal semantics and pragmatic judgments for Entailment scales. In Exerpiment 2, we asked participants to generate plausible alternatives to these items. In Experiments 3a,b we use the same experimental design for both literal semantics and pragmatic judgment tasks, however we now expand the set of scalar items to inlclude the original Entailment pairs from Experiments 1a,b with the top two alternatives generated for each scalar family by participants in Experiment 2. The orange colored items in table 1 denote additional scalar items added in Experiments 3a,b.

@@

Participants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation. Thirty participants were recruited for Experiment 3a (Literal Listener task). Data for six participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 24 participants.

Fifty participants were recruited for Experiment 3b (Pragmatic Listener task). Data for five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.

@@

Run glmer() here:
```{r}

```
To test whether literal listener compatibility judgments differed between Experiment 1a and 3a we ran a mixed effects model, regressing responses to the binary compatibility measure on scale, degree, and Experiment with random effects by subject. Results indicate (...)

Run elmer() here:
```{r}

```

To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Exerpiment with random effects by subject. Results indicate.

While conducting our analysis we realized that our literal semantic distributions for each scalar family was roughly split between two negative valenced items and two positively valenced items while more neutral alternatives appeared to be left out. (This pattern was true of all the scalar families, except for "some \ all" in which the top two alternatives were positive valenced "most" and negative valenced "none".) In Experiment 4 we explore the addition of a neutrally valenced scalar alternative for each scalar family.

# Experiment 4: Symmetric scales
In Experiment 4, we continue to extend the alternative sets, each by one additional scalar item. While we simply took the top two alternatives generated in Experiment 2 for the additional alternatives in Experiments 3a,b, in this case we chose a subjectively "neutral" valenced scalar item from among the alternatives generated in Experiment 2. The idea was to simulate a "full" set of alternatievs with negative, neutral and positive valenced items. The purple colored items in Table 1 denote additional scalar items added in Experiments 4.

## Participants
Thirty participants were recruited on Amazon Mechanical Turk and paid $0.20 for their participation. There were no data exclusions due to training failures or native language requirements, leaving a total sample of thirty participants, all native English speakers, naive to the purpose of the experiment.

@@

## Results and Discussion
Distributions for neturally valenced scalar did appear fairly gaussian, occupying a literal semantic previously unoccupied by the other alternatives.

Run glmer() here:
```{r}

```
To test whether literal listener compatibility judgments differed between Experiment 1a and 3a we ran a mixed effects model, regressing responses to the binary compatibility measure on scale, degree, and Experiment with random effects by subject. Results indicate (...)

Run elmer() here:
```{r}

```

To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Exerpiment with random effects by subject. Results indicate.

# Model Runs

Using literal semantic data from Experiments 1a, 3a and 4 we conducted three simulations with our model. Each simulation used the specific literal semantic data to specify the scale representation avaiable to our model. The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014). These data were measured in Experiment 1a. The "mid" model used the extended the original set of alternatives with the top two alternatives generated in Experiment 2. These data were measured in Exerpiment 3a. The "full" model included the full set of alternatives, including a neutral valenced alternatives. These data were measured in Experiment 4.

```{r performancePlots, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items. Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b. The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b."}
# Tuned model run data
plotData <- allModelRunData %>%
  mutate(study = ifelse(numAlts == 5, "Full", 
                        ifelse(numAlts == 4, "Top_two", "Entailment"))) %>%
  gather(Experiment, cors, c(corE6, corE11)) %>%
  mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))

@@

# Correlation scatter plot
symmetricCorPlot <- ggplot(subset(plotData, study == "Top_two"), aes(x = listener.p, y = preds)) + 
  geom_point() +
  xlab("Model predictions") +
  ylab("Human judgments") +
  stat_smooth(method = "lm") + 
  ggtitle("Model fit\nSymmetric scale")

# corBarChart

modifiedPlotData <- plotData %>%
  gather(pragStudy, pragChoice, c(9,11))
fullRepresentationFit <- qplot(stars, pragChoice, col=degree, shape = pragStudy,
      data=subset(modifiedPlotData, study == "Full")) +
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = preds), lty = 4)
fullRepresentationFit
# gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))
```

### 2016-01-21 Paper/Paper.tex
Added final model fit plot

Experiment 1a and 1b were conducted to approximate literal listener
semantic distributions (1a) and pragmatic judgments (1b) for five pairs
of scalar items taken from van Tiel (2014) (see figure 5 for stimuli).
Each pair consists of a ``weaker'' scalar term (e.g. ``some'') and a
stronger scalar term (e.g. ``all''). We are calling these ``entialment
scales''``, because they encode the assumption that a listener need only
have a the stronger alternative present to generate an enriched
interpretation of the weaker term.

@@

Participants for both tasks were recruited on Amazon Mechanical Turk and
paid \$0.20 for their participation. Thirty participants were recruited
for Experiment 1a. Data for N participants was thrown out after
participants either failed to pass two training trials or were not
native English speakers, leaving a total sample of N. Fifty participants
were recruited for experiment 1b. Data for N participants was thrown out
after participants either failed to pass two training trials or were not
native English speakers, leaving a total sample of N.

@@

The left panel of Figure 1 shows a screen shot of a trial from
Experiment 1a. Participants were presented with a target scalar item and
a star-rating (between 1-5 stars) and asked to judge the compatibility
of the scalar item and star-rating. Compatibility was assessed through a
binary ``yes/no'' response to a question of the form ``Do you think that
the person \_\_\_ed the food?" where a target scalar was presented in
the ``\_\_\_ed." Each participant was presented all scalar item and
star-rating combinations with randomization.

The right panel of Figure 1 shows a screen shot of a trial from
Experiment 1b. On each trial, participants were presented with a
one-sentence prompt containing a target scalar item such as ``Someone
said they \_\_\_ed the food." They were then asked to generate a
star-rating according to what they think the reviewer likely gave. Each
participant was presented all scalar items with randomization.

@@

The left panel of figure two shows literal semantics for each of the
scalar terms ``liked'' and ``loved'' as distributions over star-ratings.

Chi-squared test? Null results, not really important here anyway\ldots{}

@@

Using Amazon's Mechanical Turk, N workers were paid \$0.20 to
participate. n workers were dropped from the analysis because they
either failed to pass training trials or were not native English
speakers. The final sample was N workers, all of whom were naive to the
purpose of the experiment.

@@

Participants were presented a target scalar term embedded in a sentence
such as, ``In a recent restaurant review someone said they thought they
\emph{----}ed the food.'' Participants were then asked to generate
plausible alternatives by responding to the question, ``If they'd felt
differently about the food, what other words could they have used
instead of \emph{----}?'' and asked to generate three alternatives.

@@

Figure 3 plots the combined counts of alternatives generated for the
scalar items ``liked'' and ``loved.'' Alternative distributions for the
other scalar pairs (e.g.. ``good/excellent'',
``memorable/unforgettable'') were similarly long-tailed. In Experiments
3a,b we took the top two alternatives generated for each scalar item to
enrich the entailment only scales from Experiments 1a,b. In experiment 4
we further enriched the scales from Experiments 3a,b with a neutral
valence scalar chosen from the alternative sets.

@@

Participants for both studies were recruited on Amazon Mechanical Turk
and paid \$0.20 for their participation. Thirty participants were
recruited for Experiment 3a (Literal Listener task). Data for N
participants was thrown out after participants either failed to pass two
training trials or were not native English speakers, leaving a total
sample of N.

Fifty participants were recruited for Experiment 3b (Pragmatic Listener
task). Data for N participants was thrown out after participants either
failed to pass two training trials or were not native English speakers,
leaving a total sample of N.

@@

Distributional differences.

@@

Experiment 4a is identical to Experiments 1a and 3a except the set of
target scalar was expanded to include a neutral valence scalar item for
each scalar family. The purple colored items in Table 1 denote
additional scalar items added in Experiments 4.

@@

Participants for both studies were recruited on Amazon Mechanical Turk
and paid \$0.20 for their participation. Thirty participants were
recruited for Experiment 4 (Literal Listener task). Data for N
participants was thrown out after participants either failed to pass two
training trials or were not native English speakers, leaving a total
sample of N.

@@

Distributional differences.

\section{Temp section Model was here}\label{temp-section-model-was-here}

\subsubsection{Results}\label{results}

Table here

Figure 4 plots model / human correlation for our three simulations.
Alpha was tuned separately for each of these runs\ldots{}

>>>>

Experiment 1a and 1b were conducted to approximate literal listener
semantic distributions \(p_{L0}(m|u)\) (Exerpiment 1a) and pragmatic
judgments \(p_{L1}(m|u)\) (Experiment 1b) for five pairs of scalar items
taken from van Tiel (2014) (see figure 5 for stimuli). Each pair
consists of a ``weaker'' scalar term (e.g. ``some'') and a stronger
scalar term (e.g. ``all''). We are calling these ``entialment
scales''``, because they encode the assumption that a listener need only
have a the stronger alternative present to generate an enriched
interpretation of the weaker term. The grey colored items in Table 1
denote the original''entailment" items used in Experiments 1a,b.

@@

Participants for both tasks were recruited on Amazon Mechanical Turk and
paid \$0.20 for their participation. Thirty participants were recruited
for Experiment 1a. Data for two participants was thrown out during
analysis because there were not native English speakers, leaving a total
sample of 28 participants. Fifty participants were recruited for
experiment 1b. Data for 7 participants was thrown out after participants
either failed to pass two training trials or were not native English
speakers, leaving a total sample of 43 participants.

@@

The left panel of Figure 1 shows a screen shot of a trial from
Experiment 1a. Participants were presented with a target scalar item and
a star-rating (between 1-5 stars) and asked to judge the compatibility
of the scalar item and star-rating. Compatibility was assessed through a
binary ``yes/no'' response to a question of the form ``Do you think that
the person thought the food was \_\_\_\_?" where a target scalar was
presented in the ``\_\_\_\_." Each participant was presented all scalar
item and star-rating combinations with randomization.

The right panel of Figure 1 shows a screen shot of a trial from
Experiment 1b. On each trial, participants were presented with a
one-sentence prompt containing a target scalar item such as ``Someone
said they thought the food was \_\_\_\_\_.'' Participants were then
asked to generate a star-rating according to what they thought the
reviewer likely gave. Each participant was presented all scalar items
with randomization.

@@

Figure 2 plots literal listner \(p_{L0}(m|u)\) distributions obtained in
Experiments 1a, 3a and 4. Data from 1a is (\ldots{}). We see clear
variation between semantic judgments between scalar families in all the
Experiments. For example, compatibility judgments for ``memorable'' and
``forgettable'' are more similar than those for ``good / excellent'' or
``liked / loved''. We will address distributional similarity across the
studies in later sections.

@@

Using Amazon's Mechanical Turk, 30 workers were paid \$0.20 to
participate. All participants were native English speakers and naive to
the purpose of the experiment.

@@

Participants were presented a target scalar term from our original
entailment set embedded in a sentence such as, ``In a recent restaurant
review someone said they thought they the food was \_\_\_\_" with a
target scalar presented in the ``\_\_\_\_." Participants were then asked
to generate plausible alternatives by responding to the question, ``If
they'd felt differently about the food, what other words could they have
used instead of \_\_\_\_\_?'' and asked to generate three unique
alternatives.

@@

Figure 3 plots the combined counts of alternatives generated for the
scalar items ``liked'' and ``loved.'' Alternative distributions for the
other scalar pairs (e.g.. ``good/excellent'',
``memorable/unforgettable'') were similarly long-tailed, however the
size and content of the alternate sets were diverse. (SOMETHING MORE
MORE FORMAL HERE???)

@@

Participants for both studies were recruited on Amazon Mechanical Turk
and paid \$0.20 for their participation. Thirty participants were
recruited for Experiment 3a (Literal Listener task). Data for six
participants was thrown out after participants either failed to pass two
training trials or were not native English speakers, leaving a total
sample of 24 participants.

Fifty participants were recruited for Experiment 3b (Pragmatic Listener
task). Data for five participants was thrown out after participants
either failed to pass two training trials or were not native English
speakers, leaving a total sample of 45 participants.

@@

Run glmer() here:

To test whether literal listener compatibility judgments differed
between Experiment 1a and 3a we ran a mixed effects model, regressing
responses to the binary compatibility measure on scale, degree, and
Experiment with random effects by subject. Results indicate (\ldots{})

Run elmer() here:

To test whether pragmatic judgments differed between Experiments 1b and
3b we ran a mixed effects model, regressing star-rating selections on
scale, scalar item and Exerpiment with random effects by subject.
Results indicate.

While conducting our analysis we realized that our literal semantic
distributions for each scalar family was roughly split between two
negative valenced items and two positively valenced items while more
neutral alternatives appeared to be left out. (This pattern was true of
all the scalar families, except for ``some ~all'' in which the top two
alternatives were positive valenced ``most'' and negative valenced
``none''.) In Experiment 4 we explore the addition of a neutrally
valenced scalar alternative for each scalar family.

@@

In Experiment 4, we continue to extend the alternative sets, each by one
additional scalar item. While we simply took the top two alternatives
generated in Experiment 2 for the additional alternatives in Experiments
3a,b, in this case we chose a subjectively ``neutral'' valenced scalar
item from among the alternatives generated in Experiment 2. The idea was
to simulate a ``full'' set of alternatievs with negative, neutral and
positive valenced items. The purple colored items in Table 1 denote
additional scalar items added in Experiments 4.

@@

Thirty participants were recruited on Amazon Mechanical Turk and paid
\$0.20 for their participation. There were no data exclusions due to
training failures or native language requirements, leaving a total
sample of thirty participants, all native English speakers, naive to the
purpose of the experiment.

@@

Distributions for neturally valenced scalar did appear fairly gaussian,
occupying a literal semantic previously unoccupied by the other
alternatives.

Run glmer() here:

To test whether literal listener compatibility judgments differed
between Experiment 1a and 3a we ran a mixed effects model, regressing
responses to the binary compatibility measure on scale, degree, and
Experiment with random effects by subject. Results indicate (\ldots{})

Run elmer() here:

To test whether pragmatic judgments differed between Experiments 1b and
3b we ran a mixed effects model, regressing star-rating selections on
scale, scalar item and Exerpiment with random effects by subject.
Results indicate.

\section{Model Runs}\label{model-runs}

Using literal semantic data from Experiments 1a, 3a and 4 we conducted
three simulations with our model. Each simulation used the specific
literal semantic data to specify the scale representation avaiable to
our model. The ``entailment'' model used only the original pair of
scalar items pulled from van Tiel (2014). These data were measured in
Experiment 1a. The ``mid'' model used the extended the original set of
alternatives with the top two alternatives generated in Experiment 2.
These data were measured in Exerpiment 3a. The ``full'' model included
the full set of alternatives, including a neutral valenced alternatives.
These data were measured in Experiment 4.
